
% The \section{} command formats and sets the title of this
% section. We'll deal with labels later.
\section{Introduction}
\label{sec:intro}
Image processing is a vital component of computer vision and
artificial intelligence. Within image processing, image segmentation
continues to be a focus of research as machines are developed to have similar visual abilities to humans. Segmentation 
groups pixels into regions of similar characteristics, which can be used
for automated analysis, tracking, and object recognition.  Many image segmentation techniques operate on color images, grouping pixels by color or perceived luminosity.  We explore an alternative: segmentation of depth images.

Depth images contain information about the distance from a point in space to the camera sensor. While traditional RGB images contain a matrix
of color pixels, each containing a red, green, and blue value, a depth image
only contains a matrix of depth values. Depth images can be visually
rendered in greyscale, where a point of maximum distance
is represented as white and a point of minimum distance is represented
as black. The construction of accurate depth images relies heavily on recent technology, including LIDAR and infrared sensors.  Notably, the Microsoft Xbox Kinect
sensor has the ability to simultaneously record depth images and color
images, providing researchers easy access to rich depth data.

The algorithms presented below were tested and tuned using data taken by an Xbox Kinect sensor by a team from UC Berkeley and the Max Planck Institute for Informatics in their work on category-level object recognition \cite{kinect}.  As such, it presents an imperfect source of realistic, often cluttered scenes, perfect for useful algorithm development.

There are two fundamental approaches for segmenting an image: edge-based
segmentation and region-based segmentation \cite{aima}. Edge-based
segmentation locates major discontinuities in the image, indicating
separate distinguishable objects, whereas region-based segmentation
identifies different surfaces within those objects by calculating the
normal vectors at each point. The remainder of this paper covers
background information pertaining to the two methods of segmentation used,
describes our specific experimental design, and shares our results and conclusions. 

% In this section, you should introduce the reader to the problem you
% are attempting to solve. For example, for the first project: describe
% the $15$-puzzle, and why it's interesting as an A.I. problem. You
% should also cite and briefly describe other related papers that have
% tackled this problem in the past --- things that came up during the
% course of your research. In the AAAI style, citations look like
% \cite{aima} (see the comments in the source file \texttt{intro.tex} to
% see how this citation was produced). Conclude by summarizing how the
% remainder of the paper is organized. \\

% Citations: As you can see above, you create a citation by using the
% \cite{} command. Inside the braces, you provide a "key" that is
% uniue to the paper/book/resource you are citing. How do you
% associate a key with a specific paper? You do so in a separate bib
% file --- for this document, the bib file is called
% project1.bib. Open that file to continue reading...

% Note that merely hitting the "return" key will not start a new line
% in LaTeX. To break a line, you need to end it with \\. To begin a 
% new paragraph, end a line with \\, leave a blank
% line, and then start the next line (like in this example).
% Overall, the aim in this section is context-setting: what is the
% big-picture surrounding the problem you are tackling here?

